Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-03-13 paper/ms.tex
100 new words into the paper

\begin{abstract}
In this Letter we implement a new method to find the characteristic
mass of dark matter halos hosting Lyman-Alpha Emitting (LAE)
galaxies. The method is based on matching the statistics for the
cosmic variance with the observations recently obtained by
\cite{Yamada2012}. We build a model for LAEs on top of a large N-body
cosmological simulation (Bolshoi). The basic principle is that a dark
matter halo can host one LAE with a probability $f_{\rm occ}$ if its
mass is found withing a certain range mass range delimited by two
threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
hundreds of mock catalogs in a thourough exploration of the parameter
space of this model. These catalogs are constructed in such a way as
to reproduce the spatial correlation between the different observed
fields. We find that the models that best match the
observed cosmic variance statistics are those with halo masses in the
range $M_{\rm min}=$ and $M_{\rm max}=$ with and occupation fraction
that scales as $f_{\rm occ}=$ with the minimum mass. We find that the
angular correlation function is in agreement with the observational
constraints. 
\end{abstract}

@@

\subsection{Dark Matter Halo Number Density}
We present first the results for  the intergrated dark matter halo surface
density as a function of halos mass for each one o the 210 sub-volumes in
the Bolshoi simulation. This result allowsus to better understand the
expected trends for the LAEs' preferred mass and the occupation
fraction. Figure \ref{fig:laes_dist} show these results. The continous lines
correspond to the subvolumes. The shadowed area indicates the surface
density values for LAEs allowed by the observations.

From this Figure we can read which models cannot reproduce the
observations. Regions in the plot where the halo surface density
values are below the observational constraint correspond to high
masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
$M_{\rm   min}$ located in that mass range, the surface density is too
low compared with observations.

Conversely, there are regions in the plot where the halo surface
density can be higher than the observational constraints correspond to
models ${\mathcal M}$ with a minimum mass below this threshold. Models
with this minimum mass hava a chance for successfuly reproducing
observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to
lower the halo number density down to the observed value.

@@

These results distinguish three mass regimes. In the first regime, at
high mass values, we find that LAE models with minimum mass of $M_{\rm
  min}>XXX$ are not compatible with observations as expected from the
analysis in the previous subsection. Below this mass down to $M_{\rm
  min}=XXX$ any minium and maximum mass models are compatible with
LAEs observations. In a thirds mass regime, for low mass values
$M_{\rm min}<$ only a limited range of models with $M_{\rm max}$ is
able to reproduce observations.

>>>>

\begin{abstract}
In this Letter we implement a new method to find the characteristic
mass of dark matter halos hosting Lyman-Alpha Emitting (LAE)
galaxies. The method is based on matching the statistics for the
cosmic variance with the observations recently obtained by
\cite{Yamada2012}. We build a model for LAEs on top of a large N-body
cosmological simulation (Bolshoi). The basic principle is that a dark
matter halo can host one LAE with a probability $f_{\rm occ}$ if its
mass is found withing a certain range mass range delimited by two
threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
hundreds of mock catalogs in a thourough exploration of the parameter
space of this model. These catalogs are constructed in such a way as
to reproduce the spatial correlation between the different observed
fields. We find that the models that best match the observed cosmic
variance statistics are those with halo masses in the range $M_{\rm
  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales
as $f_{\rm occ}=$ with the minimum mass. We find that the angular
correlation function is in agreement with the observational
constraints mostly due to the cosmic variance in the small angular
fields where this statistics has been computed so far. We also present
predictions for future measurements of the correlation function on
larger continous fields. We make available the mock data for the best
models in a public repository.  
\end{abstract}

@@

\subsection{Dark Matter Halo Number Density}
In Figure \ref{fig:laes_dist} we present the results for  the intergrated dark matter halo surface
density as a function of halos mass for each one of the 210 sub-volumes in
the Bolshoi simulation. The continous lines correspond to the
subvolumes. The shadowed area indicates the surface density values for
LAEs allowed by the observations.

This result allows us to better understand the
expected trends for the LAEs' preferred mass and the occupation
fraction.  From this Figure we can read which models do not have a
chance reproduce the
observations. Regions in the plot where the halo surface density
values are below the observational constraint correspond to high
masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
$M_{\rm   min}> 3 \times 10^{11}$\hMsun located in that mass range,
the surface density is too low compared with observations.

Conversely, there are regions in the plot where the halo surface
density is always higher than the observational constraints correspond
to models ${\mathcal M}$ with a minimum mass below $M_{\rm min}<
3\times 10^{10}$\hMsun. Models with this minimum mass hava a chance
for successfuly reproducing observations if the occupation fraction
$f_{\rm occ}<1$ is tuned as to lower the halo number density down to
the observed value.

@@

These results distinguish three mass regimes. In the first regime, at
high mass values, we find that LAE models with minimum mass of $M_{\rm
  min}>3\times 10^{11}$\hMsun are not compatible with observations as
expected from the analysis in the previous subsection. For masses below $M_{\rm
  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
can be made compatible with observations, provided that
$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
limited range of models with $M_{\rm max}$ with occupation fraction
$f_{\rm occ}\sim 1$ is able to reproduce observations.
